---
title: "asteroid_diameter_clustering"
author: "Devyani Srivastava"
date: "2023-02-27"
output: html_document
---

**Clustering for diameter dataset**

```{r}
library(tidyverse)
library(readr)
library(cluster)
library(Hmisc)
library(ggplot2)
library(tidyr)
library(gridExtra)
library(proxy)
library(factoextra)
library(arules)
library(arulesViz)
```

```{r}
doc2_dia<-read.csv('C:/Users/devya/OneDrive/Desktop/ml_osita_codes/ml_project/Asteroid_Diameter.csv')
doc2_dia %>% head()
doc2_dia%>% names()
```

**Calculating the number of missing values in each columns**

```{r}
 tibble(names(doc2_dia),colSums(is.na(doc2_dia)))
```

Calculating the number of missing values in target variable

```{r}
  sum(!is.na(doc2_dia$diameter))
```

```{r}
doc2_dia <-doc2_dia %>% drop_na(diameter)
doc2_dia %>% dim()
```

```{r}
tibble(names(doc2_dia),colSums(is.na(doc2_dia)))
```

```{r}
doc2_dia <- doc2_dia %>% select(-c('H','albedo','name','rot_per','spec_B',
             'BV','spec_T','UB','G',
             'extent','GM','IR'))
doc2_dia %>% names()
```

```{r}
na_cols<-tibble(names(doc2_dia),colSums(is.na(doc2_dia)))
na_cols
```

```{r}
col_type<-tibble(names(doc2_dia),sapply(doc2_dia,class))
col_type
```
```{r}
doc2_dia_arm<-doc2_dia %>% select(c('class','pha','neo'))
```


```{r}
doc2_dia %>% select_if(is.character) %>% head()

```

```{r}
doc2_dia %>%arrange() %>% count(pha)
doc2_dia %>% arrange() %>% count(neo)
doc2_dia %>% arrange() %>% count(class)
```

```{r}
doc2_dia %>% arrange() %>% count(condition_code)
```

```{r}
doc2_dia$condition_code <-doc2_dia$condition_code %>% as.numeric()
```

```{r}
col_type
```

```{r}
doc2_dia %>% describe() 
```

```{r}
doc2_dia %>% hist.data.frame()
```

```{r eval=FALSE,echo=FALSE}
doc2_dia %>% ggplot()+geom_boxplot(aes(y='data_arc'))
```

```{r}
doc2_dia$data_arc <-as.numeric(doc2_dia$data_arc)
```

```{r}
doc2_dia %>% mutate(across(data_arc, ~replace_na(., median(., na.rm=TRUE))))
```

```{r}
na_cols
```

```{r}
col_type
```

```{r}
doc2_dia %>% select_if(is.character) %>% head()
```

the connection between the classifiers and the intended audience.

The physically dangerous classifer cannot be used for modeling because it is based on the target.

The NEO classifier is not required for further investigation because it is included in the more precise classifier of orbit class.

```{r}
doc2_dia <-doc2_dia %>% select(-c('neo', 'pha'))
doc2_dia %>% names()
```

\*\* for clustering we will consider unlabelled numeric features \*\*

```{r}
doc_clust<-doc2_dia %>% select(-c('class','condition_code'))
doc_clust %>% names()
```

```{r}
doc_clust<-doc_clust %>% head(2500)
```

```{r}
doc_clust_scale<-scale(doc_clust)
doc_clust_scale
```

Calculating distance

```{r}
doc_clust_dist <-dist(doc_clust_scale)
doc_clust_dist
```

```{r}
k2<- kmeans(doc_clust_scale,centers=2,nstart=25)
k3 <- kmeans(doc_clust_scale,centers=3,nstart=25)
k4 <- kmeans(doc_clust_scale,centers=4,nstart=25)
k5 <- kmeans(doc_clust_scale,centers=5,nstart=25)
k6<- kmeans(doc_clust_scale,centers=6,nstart=25)
k7<- kmeans(doc_clust_scale,centers=7,nstart=25)

```

```{r}

p1<-fviz_cluster(k2,geom='point',data=df) +ggtitle("k=2")
p2<-fviz_cluster(k3,geom='point',data=df) +ggtitle("k=3")
p3<-fviz_cluster(k4,geom='point',data=df) +ggtitle("k=4")
p4<-fviz_cluster(k5,geom='point',data=df) +ggtitle("k=5")
p5<-fviz_cluster(k6,geom='point',data=df) +ggtitle("k=6")
p6<-fviz_cluster(k7,geom='point',data=df) +ggtitle("k=7")

```

```{r}
grid.arrange(p1,p2,p3,p4,p5,p6,nrow=3)
```

```{r}
fviz_nbclust(doc_clust_scale,kmeans,method='wss') + labs(subtitle = 'Elbow Method')
```

```{r}
fviz_nbclust(doc_clust,kmeans,method='silhouette')
```
**Gap Stat Method**

```{r}
set.seed(200)
gap_stat_k <-clusGap(doc_clust,FUN=kmeans,nstart=25, K.max = 20)
print(gap_stat_k,method='firstmax')
```
**Hierarchical clustering**

```{r}
doc_clust_h<-dist(doc_clust_scale,method='cosine')
doc_clust_h 
```

```{r}
h_doc<-hclust(doc_clust_h,method='ward.D')
h_doc
```

**Plotting dendogram**

```{r}
plot(h_doc)
rect.hclust(h_doc, k=4,border = 2:5)
```

```{r}
plot(h_doc)
rect.hclust(h_doc, k=3,border = 2:6)
```
```{r}
h_doc_<-hclust(doc_clust_h,method='ward.D')
h_doc_
```


```{r}
plot(h_doc_)
rect.hclust(h_doc_, k=4,border = 2:6)
```
```{r}
h_doc_avg<-hclust(doc_clust_h,method='average')
plot(h_doc_avg)
rect.hclust(h_doc_avg, k=4,border = 2:6)
```
```{r}
h_doc_cen<-hclust(doc_clust_h,method='centroid')
plot(h_doc_cen)
rect.hclust(h_doc_cen, k=4,border = 2:6)
```



